\section{Project Management}

Project planning follows the directives captured in \texttt{todo.md}, which serves as a combined roadmap and status ledger. Weekly check-ins convert supervisory feedback into actionable tasks, while Git branches and GitHub Actions provide traceability for merged work.

\subsection{Timeline}
\begin{itemize}
    \item \textbf{Phase 0 --- Baseline Port}: Adapted the Ateniese redactable blockchain benchmark into the current modular simulator, laying the groundwork for injectable smart contracts and redaction policies. (Complete)
    \item \textbf{Phase 1 --- Infrastructure Integration}: Added configurable adapters for IPFS, EVM access, and environment management; established encryption-at-rest and content-addressable linkage between on-chain and off-chain artefacts. (Complete)
    \item \textbf{Phase 2 --- Zero-Knowledge Enablement}: Delivered the medical circuit mapper, real Groth16 proof pipeline, and proof-of-consistency tooling referenced in the latest documentation updates. (Complete)
    \item \textbf{Phase 3 --- Contract Orchestration}: In progress. Outstanding tasks include wiring contract-based execution of redactions, finalising censored dataset publication, and broadening test coverage to negative cases.
\end{itemize}

\subsection{Team Roles}
Core development is led by Enrico Pezzano, who coordinates implementation across Python, Solidity, and circom. The Mobile IoT Security Lab reviewers provide design oversight, approve roadmap adjustments, and evaluate compliance alignment. Collaboration occurs via issue tracking in \texttt{todo.md}, code reviews on the GitHub repository, and synchronous milestone reviews when introducing new cryptographic components.

\subsection{Risk Management}
\begin{itemize}
    \item \textbf{Proof Artefact Drift}: High impact. Mitigated by mandating checksum validation for \texttt{circuits/build/} artefacts and by failing fast when snarkjs binaries or zkeys are missing.
    \item \textbf{Regulatory Misalignment}: Medium impact. Addressed through explicit policy modelling in \texttt{MedicalDataContract} and by mapping requirements back to GDPR/HIPAA directives in backlog items.
    \item \textbf{External Dependency Availability}: Medium impact. Environment flags (\texttt{USE\_REAL\_IPFS}, \texttt{USE\_REAL\_EVM}) allow fallbacks to simulators, ensuring development remains unblocked when IPFS nodes or EVM endpoints are offline.
    \item \textbf{Security of Off-Chain Storage}: Medium impact. Countered by encrypting data before IPFS upload and by treating key rotation plus unpinning as first-class parts of the redaction workflow.
\end{itemize}
